Reaction & action alternatives

### 2023-08-03 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/reaction_action_alternatives.Rmd
bla

# REACTION 
df_reaction <- read_excel("data/coding_reactions_MK.xlsx") %>% 
  janitor::clean_names() %>%
  mutate(reaction = as.numeric(case_when(code > 3 ~ '0',
                                         code <= 3 ~ '1',
                                         TRUE ~ 'F')
                               )
         ) %>% 
  select(id, reaction)

>>>>

# REACTION ALTERNATIVE
df_reaction <- read_excel("data/coding_reactions_MK.xlsx") %>% 
  janitor::clean_names() %>%
  mutate(reaction = as.numeric(case_when(code > 3 ~ '0',
                                         code <= 3 ~ '1',
                                         TRUE ~ 'F')
                               )
         ) %>% 
  select(id, reaction)
